---
title: "Assignment6"
author: "Joyce Aldrich"
date: "2022-10-30"
output: html_document
---

Assignment: 
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You’ll need to start by signing up for an API key.
Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and
transform it into an R DataFrame.

```{r}
library(httr)
library(jsonlite)
library(dplyr)
```

#store url and api key
```{r}
url<- "https://api.nytimes.com/svc/movies/v2/reviews/search.json?api-key=HuVC3AH85KUOLicBXhObdKaPA1P6jWzI"
```
# get function to retreive data 
```{r}
movies <-GET(url)
```
#confirm the status
```{r}
movies$status_code
```
# store the text format of content
```{r}
text_content <- content(movies, "text")
```

# covert to dataframe
```{r}
json_content_df <- text_content %>% fromJSON() %>% as.data.frame()
```

# display the data frame 
```{r}
dim(json_content_df)
head(json_content_df)
```



